{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-10-09 thesis/future.tex
rearrange quotes and add one from 17776

\chapter{Future Work}
\label{chap:warpzone}
\inspirationalquote{
\begin{tabular}{p{0.75\textwidth}}
We can't be free until we learn to laugh at ourselves.
Once you look in the mirror and see just how foolish we can be,
laughter is inevitable.
And from laughter comes wisdom.
\end{tabular}}
{G'Kar, Babylon 5}

>>>>

\chapter{Future Work}
\label{chap:warpzone}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}

### 2018-10-09 thesis/thesis.tex
i have a date now
real keywords
rearrange quotes and add one from 17776

\title{ %% {\it \huge Thesis Proposal}\\
{\bf Practical Concurrency Testing} \\
\normalsize \vspace{1em}
\begin{tabular}{c}
{\em or: How I Learned to Stop Worrying and Love the Exponential Explosion}
\end{tabular}}
\author{Ben Blum}
\date{Decembruary 2018}
\Year{2018}
\trnumber{}

@@

\keywords{landslide terminal, baggage claim, ground transportation, ticketing}

@@

\chapter{Conclusion}
\label{chap:conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}

>>>>

\title{ %% {\it \huge Thesis Proposal}\\
{\bf Practical Concurrency Testing} \\
\normalsize \vspace{1em}
\begin{tabular}{c}
{\em or: How I Learned to Stop Worrying and Love the Exponential Explosion}
\end{tabular}}
\author{Ben Blum}
\date{October 2018}
\Year{2018}
\trnumber{}

@@

%\keywords{landslide terminal, baggage claim, ground transportation, ticketing}
\keywords{concurrency, debugging, verification, model checking, data races, education, transactional memory}

@@

\chapter{Conclusion}
\label{chap:conclusion}
\inspirationalquote{
\begin{tabular}{p{0.6\textwidth}}
"This is the end, right? The end of this story?"

"We were always at the end. It's a free play, buddy. Clock's all zeroes."
\end{tabular}}
%{Nine \& Ten, 17776}
{17776}
